%% \documentclass{sig-alternate}
\documentclass[conference]{IEEEtran}

\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{times}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{url}
\usepackage{txfonts}
\usepackage{xspace}
\usepackage{float}
\usepackage{latexsym}
%\usepackage{natbib}
\usepackage{alltt}
\usepackage{color}
\usepackage{textcomp}
\usepackage{balance}
%\usepackage[pass,letterpaper]{geometry}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{enumitem}

\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\usepackage[pass]{geometry}
\setlength{\textfloatsep}{0.4\baselineskip}

\begin{document}

\newcommand{\ie}{\textit{i.e.,} }
\newcommand{\eg}{\textit{e.g.,} }
\newcommand{\subject}[1]{\texttt{\small #1}}
\newcommand{\rules}{{\mathcal R}}
\newcommand{\tests}{{\mathcal T}}
\newcommand{\elemexists}{\mt{exists}}
\newcommand{\elemenabled}{\mt{enabled}}
\newcommand{\elemexplored}{\mt{explored}}
\newcommand{\note}[1]{{\color{red}$[$ \bf #1 $]$}}
\newcommand{\lang}[1]{\texttt{\scriptsize #1}}
\newcommand{\tool}{\textsc{buster}}
\newcommand{\exhaust}{\textsc{exhaust}}
\newcommand{\choco}{\textsc{choco}}
\newcommand{\wateg}{\textsc{wateg}}

\title{Test Generation from Business Rules}

\author{
\IEEEauthorblockN{Simon Holm Jensen}
\IEEEauthorblockA{Snowflake Computing \\ simon@hjensen.net}
\and
\IEEEauthorblockN{Suresh Thummalapenta}
\IEEEauthorblockA{Microsoft Corporation \\ suthumma@microsoft.com}
\and
\IEEEauthorblockN{Saurabh Sinha}
\IEEEauthorblockA{IBM Research \\ saurabhsinha@in.ibm.com}
\and
\IEEEauthorblockN{Satish Chandra}
\IEEEauthorblockA{Samsung Research America \\ schandra@samsung.com}
}

%% \numberofauthors{4}
%% \author{
%% \alignauthor Simon Holm Jensen \\
%% \affaddr{Samsung Research America}\\
%% \email{s.jensen@samsung.com} 
%% \alignauthor Suresh Thummalapenta \\
%% \affaddr{Microsoft Corporation} \\
%% \email{suthumma@microsoft.com}
%% \alignauthor Saurabh Sinha \\
%% \affaddr{IBM Research India} \\
%% \email{saurabhsinha@in.ibm.com}
%% \and 
%% \alignauthor Satish Chandra \\
%% \affaddr{Samsung Research America} \\
%% \email{schandra@samsung.com}
%% }

\maketitle

\begin{abstract}
Enterprise applications are difficult to test because their intended
functionality is either not described precisely enough or described in
cumbersome business rules. It takes a lot of effort on the part of a test
architect to understand all the business rules and design tests that ``cover''
them, \ie exercise all their constituent scenarios. Part of the problem is that
it takes a complicated set up sequence to drive an application to a state in
which a business rule can even fire.  In this paper, we present a business rule
modeling language that can be used to capture functional specification of an
enterprise system. The language makes it possible to build tool support for rule
authoring, so that obvious deficiencies in rules can be detected
mechanically. Most importantly, we show how to mechanically generate test
sequences---\ie test steps and test data---needed to exercise these business
rules. To this end, we translate the rules into logical formulae and use
constraint solving to generate test sequences.  One of our contributions is to
overcome scalability issues in this process, and we do this by using a novel
algorithm for organizing search through the space of candidate sequences to
discover covering sequences.  Our results on three case studies show the promise
of our approach.
\end{abstract}

\input{intro}
\input{model}
\input{example}
\input{algorithm}
\input{evaluation}
\input{related}
\input{conclusion}

\bibliographystyle{IEEEtran}
{\small
\bibliography{paper}
}
\end{document}
